On the error performance of the $A_n$ lattices

### 2012-03-19 other/threepager/threepager.tex
added modified stuff for the threepager.tex

%\documentclass[a4paper,10pt]{article}
%\documentclass[draftcls, onecolumn, 11pt]{IEEEtran}
%\documentclass[journal, onecolumn, 10pt]{IEEEtran}
\documentclass[journal]{../../IEEEtran}
%\documentclass[correspondence,9pt]{IEEEtran}

\usepackage{../../mathbf-abbrevs}
\usepackage{amsmath}
\DeclareMathOperator{\argmin}{\arg\!\min}

@@

%opening
\title{On the error performance of the $A_n$ lattices}
\author{Robby McKilliam, Ramanan Subramanian, Emanuele Viterbo, I. Vaughan L. Clarkson
 \thanks{Robby~McKilliam and Ramanan Subramanian are with the Institute for Telecommunications Research, The University of South Australia, SA, 5095.  Emanuele Viterbo is with the Department of Electrical and Computer Systems Engineering, Monash University, Melbourne, VIC, Australia.   Vaughan~Clarkson is with the School of Information Technology \& Electrical Engineering, The University of Queensland, QLD., 4072, Australia.  A preliminary full version of this paper is available at http://arxiv.org/abs/1111.6334.}
}

@@

@@

\maketitle

\begin{abstract}
We consider the root lattice $A_n$ and derive explicit formulae for the moments of its Voronoi cell.  These formulae enable accurate prediction of the error probability of lattice codes constructed from $A_n$.
\end{abstract}

\begin{keywords}
Lattices, lattice decoding, root lattice, probability of error, Voronoi cell.
\end{keywords}

\section{Introduction}\label{sec:introduction}

@@

\section{The lattice $A_n$}\label{sec:lattice-a_n}
Let $H$ be the hyperplane orthogonal to the all ones vector of length $n+1$, denoted by $\onebf$, that is
\[
\onebf = \left[ \begin{array}{cccc} 1 & 1 & \cdots & 1 \end{array} \right]^\prime,
\]
where superscript $^\prime$ indicates the transpose.  Any vector in $H$ has the property that the sum of its elements is zero and for this reason $H$ is often referred to as the \emph{zero-sum plane}.  The lattice $A_n$ is the intersection of the integer lattice $\ints^{n+1}$ with the zero-sum plane, that is
\begin{equation}
\label{eq:An_sub_Zn}
  A_{n} = \ints^{n+1} \cap H = \big\{ \xbf \in \ints^{n+1} \mid \dotprod{\xbf}{\onebf} = 0  \big\}.
\end{equation}
Equivalently, $A_n$ consists of all of those points in $\ints^{n+1}$ with coordinate sum equal to zero.
% A generator matrix for $A_n$ is the $(n+1)\times n$ matrix
% \[
% \left[ \begin{array}{rrrrrrr}
% 1 & 0 & 0 &  \cdots & 0 & 0 \\
% -1 & 1 & 0 &  \cdots & 0 & 0 \\
% 0 & -1 & 1 &  \cdots & 0 & 0 \\
% 0 & 0 & -1 & \cdots & 0 & 0 \\
% \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
% 0 & 0 & 0 & \cdots & -1 & 1 \\
% 0 & 0 & 0 & \cdots & 0 & -1  \\
% \end{array} \right].
% \]
In two dimensions $A_2$ is the hexagonal lattice (Figure~\ref{fig:hexlatfig}), and in three dimension $A_3$ is the body centered cubic lattice~\cite[p. 108]{SPLAG}.  These are the densest known sphere packings in dimensions two and three.

\begin{figure}[tbp]
	\centering
		\includegraphics[width=\linewidth]{hexlatfig-1.mps}
		\caption{The hexagonal lattice $A_2$.  The Voronoi cell is a regular hexagon.}
		\label{fig:hexlatfig}
\end{figure}

@@

\section{Conclusion}

Recursive formulae for the moments of the Voronoi cell of the lattice $A_n$ were found.  These enable accurate prediction of the performance of codes constructed from $A_n$.  In two dimensions $A_2$ is the hexagonal lattice and in three dimensions $A_3$ is the face-centered cubic lattice.  Our results include codes constructed using these packings as a special case.  %The lattice $A_n$ does not produce good codes in large dimension, but we are hopeful that the techniques developed here can be applied to other lattices.  In particular similar techniques might apply to the family Coxeter lattices, which contains the root lattice $E_8$.

>>>>

%\documentclass[a4paper,10pt]{article}
%\documentclass[draftcls, onecolumn, 11pt]{IEEEtran}
%\documentclass[journal, onecolumn, 10pt]{IEEEtran}
%\documentclass[journal]{../../IEEEtran}

\documentclass[final]{proceedings}
%\documentclass[correspondence,9pt]{IEEEtran}

\usepackage{crop}
\crop
%\makeindex

\usepackage{../../mathbf-abbrevs}
%\usepackage{amsmath}
\newcommand{\argmin}{\arg\!\min}

@@

%\title{On the error performance of the $A_n$ lattices}
%\author{Robby McKilliam, Ramanan Subramanian, Emanuele Viterbo, I. Vaughan L. Clarkson
 %\thanks{Robby~McKilliam and Ramanan Subramanian are with the Institute for Telecommunications Research, The University of South Australia, SA, 5095.  Emanuele Viterbo is %with the Department of Electrical and Computer Systems Engineering, Monash University, Melbourne, VIC, Australia.   Vaughan~Clarkson is with the School of Information %Technology \& Electrical Engineering, The University of Queensland, QLD., 4072, Australia.  A preliminary full version of this paper is available at http://arxiv.org/abs/1111.6334.}
%}

@@

%opening
\chapter[On the error performance of the $A_n$ lattices]{On the error performance of the $A_n$ lattices}

\begin{authorline}
Robby McKilliam, Ramanan Subramanian, Emanuele Viterbo and I. Vaughan L. Clarkson\thanks{Robby~McKilliam and Ramanan Subramanian are with the Institute for Telecommunications Research, The University of South Australia, SA, 5095.  Emanuele Viterbo is with the Department of Electrical and Computer Systems Engineering, Monash University, Melbourne, VIC, Australia.   Vaughan~Clarkson is with the School of Information Technology \& Electrical Engineering, The University of Queensland, QLD., 4072, Australia.  A preliminary full version of this paper is available at http://arxiv.org/abs/1111.6334.}
\end{authorline}

@@

@@

\section{The lattice $A_n$}\label{sec:lattice-a_n}
Let $H$ be the hyperplane orthogonal to the all ones vector of length $n+1$, denoted by $\onebf$, that is
\[
\onebf = \left[ \begin{array}{cccc} 1 & 1 & \cdots & 1 \end{array} \right]^\prime,
\]
where superscript $^\prime$ indicates the transpose.  Any vector in $H$ has the property that the sum of its elements is zero and for this reason $H$ is often referred to as the \emph{zero-sum plane}.  The lattice $A_n$ is the intersection of the integer lattice $\ints^{n+1}$ with the zero-sum plane, that is
\begin{equation}
\label{eq:An_sub_Zn}
  A_{n} = \ints^{n+1} \cap H = \big\{ \xbf \in \ints^{n+1} \mid \dotprod{\xbf}{\onebf} = 0  \big\}.
\end{equation}
Equivalently, $A_n$ consists of all of those points in $\ints^{n+1}$ with coordinate sum equal to zero.
% A generator matrix for $A_n$ is the $(n+1)\times n$ matrix
% \[
% \left[ \begin{array}{rrrrrrr}
% 1 & 0 & 0 &  \cdots & 0 & 0 \\
% -1 & 1 & 0 &  \cdots & 0 & 0 \\
% 0 & -1 & 1 &  \cdots & 0 & 0 \\
% 0 & 0 & -1 & \cdots & 0 & 0 \\
% \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
% 0 & 0 & 0 & \cdots & -1 & 1 \\
% 0 & 0 & 0 & \cdots & 0 & -1  \\
% \end{array} \right].
% \]
In two dimensions $A_2$ is the hexagonal lattice, and in three dimension $A_3$ is the body centered cubic lattice~\cite[p. 108]{SPLAG}.  These are the densest known sphere packings in dimensions two and three.

%\begin{figure}[tbp]
%	\centering
%		\includegraphics[width=\linewidth]{hexlatfig-1.mps}
%		\caption{The hexagonal lattice $A_2$.  The Voronoi cell is a regular hexagon.}
%		\label{fig:hexlatfig}
%\end{figure}

@@

%\section{Conclusion}

%Recursive formulae for the moments of the Voronoi cell of the lattice $A_n$ were found.  These enable accurate prediction of the performance of codes constructed from $A_n$.  In two dimensions $A_2$ is the hexagonal lattice and in three dimensions $A_3$ is the face-centered cubic lattice.  Our results include codes constructed using these packings as a special case.  %The lattice $A_n$ does not produce good codes in large dimension, but we are hopeful that the techniques developed here can be applied to other lattices.  In particular similar techniques might apply to the family Coxeter lattices, which contains the root lattice $E_8$.
